Field-informed Reinforcement Learning for Learning Large-Scale Collective Tasks

### 2023-05-18 paper.tex

L = \begin{cases}

@@

where $y$ is the expected location, $\hat{y}$ represents the ground truth, and $\delta$ is a dedicated threshold. \lukas{what is the value of $\delta$ in the training?}

>>>>

L_\delta = \begin{cases}

@@

where $\delta$ is a hyperparameter that determines the threshold between the two loss functions and $y$ and $\hat{y}$ are the target and predicted values, respectively.
This function is used to penalise the agent if the action taken is too far from the optimal action. 
\lukas{what is the value of $\delta$ in the training?}
